Fusing Filters with Integer Linear Programming

### 2014-05-12 2014betterfusionforfilters/section/04-ILP.tex
note sum1 sum2 example in ilp different types

As a degenerate example, consider fusing an operation on filtered data with its generating filter:
\begin{code}
gts  = filter (>0) us
sum2 = fold (+) 0  gts
\end{code}
Here, $parents(gts,sum2) = \{gts, gts\}$.
This generates spurious, but still valid, constraints that $gts$ must be fused with $gts$ and $gts$ must be fused with $sum2$, in order for $gts$ and $sum2$ to be fused together.
While these constraints are unnecessary in this case, they are harmless.

>>>>

As a degenerate example, consider fusing an operation on filtered data with its generating filter:
\begin{code}
sum1 = fold (+) 0  us
gts  = filter (>0) us
sum2 = fold (+) 0  gts
\end{code}
Here, $parents(gts,sum2) = \{gts, gts\}$.
This generates spurious, but still valid, constraints that $gts$ must be fused with $gts$ and $gts$ must be fused with $sum2$, in order for $gts$ and $sum2$ to be fused together.
While these constraints are unnecessary in this case, they are harmless.

In the same example, $sum1$ and $sum2$ also have different iteration sizes.
We have that $parents(sum1,sum2) = \{sum1, gts\}$.
This means that $sum1$ and $sum2$ may only be fused if $sum1$ is fused with $sum1$ (trivial), $sum2$ is fused with $gts$, and $sum1$ is fused with $gts$.
While it may seem like these constraints should be implied by transitivity of clustering, all clustering variables are used for the objective function.
